\documentclass[footexclude,twocolumn,DIV25,fontsize=10pt]{scrreprt} 

% Author: Fogus (based on Steve Tayon's Clojure and David Liebke's Incanter cheat sheets)
% Comments, errors, suggestions: fogus -at- clojure -dot- com

% License
% Eclipse Public License v1.0
% http://opensource.org/licenses/eclipse-1.0.php

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{verbatim}
\usepackage[table]{xcolor}

% Set column space
\setlength{\columnsep}{0.25em}

% Define colours
\definecolorset{hsb}{}{}{red,0,.6,0.95;orange,.1,.6,0.95;green,.25,.6,0.95;yellow,.15,.6,0.95;blue,.55,.6,0.95;purple,.7,.6,0.95;pink,.8,.6,0.95;blue2,.58,.6,0.95;magenta,.9,.6,0.95;green2,.29,.6,0.95}

\definecolor{Brown}{cmyk}{0,0.81,1,0.60}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{CadetBlue}{cmyk}{0.62,0.57,0.23,0}
\definecolor{lightlightgray}{gray}{0.9}

% Redefine sections
\makeatletter
\renewcommand{\section}{\@startsection{section}{1}{0mm}
  {-1.7ex}{0.7ex}{\normalfont\large\bfseries}}
\renewcommand{\subsection}{\@startsection{subsection}{2}{0mm}
  {-1.7ex}{0.5ex}{\normalfont\normalsize\bfseries}}
\makeatother

% No section numbers
\setcounter{secnumdepth}{0}

% No indentation
\setlength{\parindent}{0em}

% No header and footer
\pagestyle{empty}


% A few shortcuts
\newcommand{\cmd}[1] {\texttt{\textbf{{#1}}}}
\newcommand{\cmdline}[1] {
  \begin{tabularx}{\hsize}{X}
    \texttt{\textbf{{#1}}}
    \end{tabularx}
}

\newcommand{\colouredbox}[2] {
  \colorbox{#1!40}{
    \begin{minipage}{0.95\linewidth}
      {
        \rowcolors[]{1}{#1!20}{#1!10}
        #2
        }
      \end{minipage}
    }
}

\usepackage{color}
\usepackage{xcolor}
\usepackage{listings}
\usepackage[small,bf]{caption}

\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{yellow}{\parbox{0.95\linewidth}{\hspace{15pt}#1#2#3}}}
\captionsetup[lstlisting]{format=listing}

\begin{document}

\centerline{\Large{\textbf{ClojureScript Cheat Sheet}}}
\centerline{{\large{\textbf{\textit{http://github.com/clojure/clojurescript}}}}}

\colouredbox{purple}{
\section{Documentation}
\begin{tabularx}{\hsize}{lX}
\textmd{\textrm{http://github.com/clojure/clojurescript/wiki}} & \\
\textmd{\textrm{http://www.clojurescript.net}} & \\
\textmd{\textrm{http://www.clojuredocs.org}} & \\
\end{tabularx}
}

\lstset{
language=Lisp,                             % Code langugage
basicstyle=\ttfamily,
keywordstyle=\color{OliveGreen},
morekeywords={require, use, ns, require-macros, use-macros, as, only},
frame=none,
}


\colouredbox{yellow}{
\section{Namespace Declaration}
\begin{tabularx}{\hsize}{lX}
\cmd{(ns my-cool-lib } &\\
\cmd{  (:require [some-lib :as lib]) } &\\
\cmd{  (:use [another-lib :only (a-func)]) } &\\
\cmd{  (:require-macros [my.macros :as macs]) } &\\
\cmd{  (:use-macros [mo.macs :only (my-mac)])) } &\\
\end{tabularx}

}


\colouredbox{red}{
\section{Rich Data Literals}
\begin{tabularx}{\hsize}{lX}
Maps: & \cmd{\{:key1 :val1, :key2 :val2\}} \\
Vectors: & \cmd{[1 2 3 4 :a :b :c 1 2]} \\
Sets: & \cmd{\#\{:a :b :c 1 2 3\}} \\
Truth/nullity: & \cmd{true, false, nil} \\
Keywords: & \cmd{:kw, :a-2, :prefix/kw, ::pi} \\
Symbols: & \cmd{sym, sym-2, prefix/sym} \\
Characters: & \cmd{\textbackslash a, \textbackslash u1123, \textbackslash space, \textbackslash newline} \\
Numbers/Strings: & same as in JavaScript \\
RegEx: & \cmd{\#"[Cc]lojure[Ss]cript"} \\
\end{tabularx}

}


\colouredbox{blue}{
\section{Frequently Used Functions \& Macros}
\subsection{Functions}
\begin{tabularx}{\hsize}{lX}
Math:& \cmd{+ - * / quot rem mod inc dec max min}\\
Comparison:& \cmd{= == not= < > <= >=}\\
Tests:& \cmd{nil? identical? zero? pos? neg? even? odd? true? false? nil?} \\
Keywords:& \cmd{keyword keyword?} \\
Symbols:& \cmd{symbol symbol? gensym} \\
Data Processing:& \cmd{map reduce filter partition split-at split-with} \\
Data Create:& \cmd{vector vec hash-map set list list* for} \\
Data Examination:& \cmd{first rest count get nth get get-in contains? find keys vals} \\
Data Manipulation:& \cmd{seq into conj cons assoc assoc-in dissoc zipmap merge merge-with select-keys update-in}\\
Arrays:& \cmd{into-array to-array aget aset amap areduce alength}\\
\end{tabularx}

\subsection{Macros}
\begin{tabularx}{\hsize}{lX}
Defining:& \cmd{defmacro}\\
Implementation:& Must be written in Clojure \\
Emission:& Must emit ClojureScript \\
Macros:& \cmd{if if-let cond and or -> ->> doto when when-let ..}\\
\end{tabularx}

\subsection{Extra ClojureScript Libraries}
\begin{tabularx}{\hsize}{lX}
\cmd{clojure.\{string set zipper\}} & \\
\cmd{clojure.browser.\{dom event net repl\}} & \\
\end{tabularx}

}


\colouredbox{magenta}{
\section{Abstraction (http://clojure.org/protocols)}

\subsection{Protocols}
\begin{tabularx}{\hsize}{lX}
Definition:& \cmd{(defprotocol Slicey} \\
& \cmd{  (slice [at]))} \\
Extend:& \cmd{(extend-type js/String}\\
& \cmd{  Slicey (slice [at] ...))} \\
Extend null:& \cmd{(extend-type nil}\\
& \cmd{  Slicey (slice [\_] nil))} \\
Reify:& \cmd{(reify Slicey (slice [at] ...))}\\
\end{tabularx}

\subsection{Records}
\begin{tabularx}{\hsize}{lX}
Definition:& \cmd{(defrecord Pair [h t])} \\
Access:& \cmd{(:h (Pair. 1 2)) ;=> 1} \\
Constructing:& \cmd{Pair.  ->Pair  map->Pair} \\
\end{tabularx}

\subsection{Types}
\begin{tabularx}{\hsize}{lX}
Definition:& \cmd{(deftype Pair [h t])} \\
Access:& \cmd{(.-h (Pair. 1 2)) ;=> 1} \\
Constructing:& \cmd{Pair. ->Pair} \\
With Method(s):& \cmd{(deftype Pair [h t] Object (toString [] ...))} \\
\end{tabularx}

\subsection{Multimethods}
\begin{tabularx}{\hsize}{lX}
Definition:& \cmd{(defmulti my-mm dispatch-function)}\\
Method Define:& \cmd{(defmethod my-mm :dispatch-value [args] ...)}\\
\end{tabularx}

}

\colouredbox{green2}{
\section{JS Interop (http://fogus.me/cljs-js)}
\begin{tabularx}{\hsize}{lX}
Method Call: & \cmd{(.meth obj args)} \\
  & \cmd{(. obj (meth args))} \\
Property Access:  & \cmd{(.-prop obj)} \\
  & \cmd{(. obj -prop)} \\
  & \cmd{(aget obj prop-str)} \\
Set Property: & \cmd{(set! (.-prop obj) val)} \\
 & \cmd{(aset obj prop-str val)} \\
Set Array element: & \cmd{(aset arr idx val)} \\
JS Global Access: & \cmd{js/window} \\
JS \cmd{this}: & \cmd{(this-as me (.method me))} \\
Create JS Object: & \cmd{(js-obj)} \\
Create JS Array: & \cmd{(array var-args)  (make-array size)} \\
Transf. JS value: & \cmd{(js->clj js-val)} \\
Transf. CLJ value: & \cmd{(clj->js clj-val)} \\
\end{tabularx}

}


\colouredbox{red}{
\section{Compilation (http://fogus.me/cljsc)}
\begin{tabularx}{\hsize}{lX}
Compile: & \cmdline{cljsc src-home '\{:optimizations :simple :pretty-print true\}'} \\
Adv. Compile: & \cmdline{cljsc src-home '\{:optimizations :advanced\}'} \\
\end{tabularx}

}


\colouredbox{green}{
\section{Other Useful Libraries}
\begin{tabularx}{\hsize}{lX}
Lein build: & https://github.com/emezeske/lein-cljsbuild \\
Client/Server: & http://github.com/cemerick/shoreleave-remote-ring \\
DOM: & http://github.com/levand/domina \\
jQuery: & http://github.com/ibdknox/jayq \\
Templating: & https://github.com/Prismatic/dommy \\
\end{tabularx}

}


\begin{flushright}
\footnotesize
\rule{0.7\linewidth}{0.25pt}
\verb!$Revision: 1.0, $Date: Feb 08, 2012!\\
\verb!Fogus (fogus -at- clojure -dot- com)!
\end{flushright}
\end{document}
